Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-03-25 WSSSPE1_report/WSSSPE1_summary_report.tex
removing section 7 for now
small wording change

\section{Other Discussion} \label{sec:other}

\note{from the misc questions/answers/observations part of the google doc?}

\note{all to put notes here of stuff that doesn't fit elsewhere, if any}

\todo{perhaps remove this section}

@@

For the purpose of studying software case studies, we classify the software
projects discussed in the workshop in two broad categories. First, the utility
software, comprising software tools that enable and/or facilitate the
development of other tools and techniques to carry out scientific work. This
includes the software developed to efficiently utilize new research
infrastructures.  Second, the scientific software, comprising software that was
developed with an aim to solve a class of scientific problems.

>>>>

%\section{Other Discussion} \label{sec:other}
%
%\note{from the misc questions/answers/observations part of the google doc?}
%
%\note{all to put notes here of stuff that doesn't fit elsewhere, if any}
%
%\todo{perhaps remove this section}

@@

For the purpose of studying software case studies, we classify the software
projects discussed in the workshop in two broad categories. First, utility
software, comprising software tools that enable and/or facilitate the
development of other tools and techniques to carry out scientific work. This
includes the software developed to efficiently utilize new research
infrastructures.  Second, scientific software, comprising software that was
developed with an aim to solve a class of scientific problems.
